---
title: "CodeBook"
author: "ThierryFauret"
date: "7 février 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
""

# CodeBook

## Description of the data base

The data base has 180 rows and 81 columns.
The columns are defined below.

## List of variables

|    Variable Name            | Designation                 |  TYpe of variable |         Values              | 
|-----------------------------|:---------------------------:|:-----------------:|:----------------------------|
| subject                     | Number which identifies     |Factor             |"1"  to "30"                 |
|                             |the Subject                  |30 values          |                             |
|                             |                             |                   |                             |
| label.activity              | Designation of the activity |Factor             |LAYING                       |
|                             |                             |6 factors          |STANDING                     |
|                             |                             |                   |SITTING                      |
|                             |                             |                   |WALKING                      |
|                             |                             |                   |WALKING_DOWNSTAIRS           |
|                             |                             |                   |WALKING_UPSTAIRS             |
|                             |                             |                   |                             |
|fBodyAcc.mean.X              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.mean.Y              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.mean.Z              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.meanFreq.X          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.meanFreq.Y          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.meanFreq.Z          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.std.X               |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.std.Y               |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAcc.std.Z               |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.mean.X          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.mean.Y          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.mean.Z          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.meanFreq.X      |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.meanFreq.Y      |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.meanFreq.Z      |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.std.X           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.std.Y           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccJerk.std.Z           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccMag.mean             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccMag.meanFreq         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyAccMag.std              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyAccJerkMag.mean     |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyAccJerkMag.meanFreq |mean.value of the parameter  |double             | bewteen -1 and 1            |     
|fBodyBodyAccJerkMag.std      |mean.value of the parameter  |double             | bewteen -1 and 1            |      
|fBodyBodyGyroJerkMag.mean    |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyGyroJerkMag.meanFreq|mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyGyroJerkMag.std     |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyGyroMag.mean        |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyGyroMag.meanFreq    |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyBodyGyroMag.std         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.mean.X             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.mean.Y             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.mean.Z             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.meanFreq.X         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.meanFreq.Y         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.meanFreq.Z         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.std.X              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.std.Y              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|fBodyGyro.std.Z              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAcc.mean.X              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAcc.mean.Y              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAcc.mean.Z              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAcc.std.X               |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAcc.std.Y               |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAcc.std.Z               |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerk.mean.X          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerk.mean.Y          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerk.mean.Z          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerk.std.X           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerk.std.Y           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerk.std.Z           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerkMag.mean         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccJerkMag.std          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccMag.mean             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyAccMag.std              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyro.mean.X             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyro.mean.Y             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyro.mean.Z             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyro.std.X              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyro.std.Y              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyro.std.Z              |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerk.mean.X         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerk.mean.Y         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerk.mean.Z         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerk.std.X          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerk.std.Y          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerk.std.Z          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerkMag.mean        |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroJerkMag.std         |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroMag.mean            |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tBodyGyroMag.std             |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAcc.mean.X           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAcc.mean.Y           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAcc.mean.Z           |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAcc.std.X            |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAcc.std.Y            |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAcc.std.Z            |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAccMag.mean          |mean.value of the parameter  |double             | bewteen -1 and 1            |
|tGravityAccMag.std           |mean.value of the parameter  |double             | bewteen -1 and 1            |


```{r cars}
```


