---
title: "CodeBook"
author: "ThierryFauret"
date: "5 février 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
""

# CodeBook

## Description of the data base

The data base has 14220 rows and 4 columns.
The columns has defined below.

## List of variables

|    Variable Name    | Designation                          |  TYpe of variable |         Values              | 
|---------------------|:------------------------------------:|:-----------------:|:----------------------------|
| subject             | Number which identifies the Subject  |Factor             |"1"  to "30"                 |
|                     |                                      |30 values          |                             |
|                     |                                      |                   |                             |
| label.activity      | Designation of the activities        |Factor             |LAYING                       |
|                     |                                      |6 vaues            |SITTING                      |
|                     |                                      |                   |STANDING                     |
|                     |                                      |                   |WALKING                      |
|                     |                                      |                   |WALKING_DOWNSTAIRS           |
|                     |                                      |                   |WALKING_UPSTAIRS             |
|                     |                                      |                   |                             |
|label.feature        |Designation of the  calculated        |Factor             |fBodyAcc.mean.X              |
|                     |parameters for several features       |79 values          |fBodyAcc.mean.Y              |
|                     |                                      |                   |fBodyAcc.mean.Z              |
|                     |                                      |                   |fBodyAcc.meanFreq.X          |
|                     |                                      |                   |fBodyAcc.meanFreq.Y          |
|                     |                                      |                   |fBodyAcc.meanFreq.Z          |
|                     |                                      |                   |fBodyAcc.std.X               |
|                     |                                      |                   |fBodyAcc.std.Y               |
|                     |                                      |                   |fBodyAcc.std.Z               |
|                     |                                      |                   |fBodyAccJerk.mean.X          |
|                     |                                      |                   |fBodyAccJerk.mean.Y          |
|                     |                                      |                   |fBodyAccJerk.mean.Z          |
|                     |                                      |                   |fBodyAccJerk.meanFreq.X      |
|                     |                                      |                   |fBodyAccJerk.meanFreq.Y      |
|                     |                                      |                   |fBodyAccJerk.meanFreq.Z      |
|                     |                                      |                   |fBodyAccJerk.std.X           |
|                     |                                      |                   |fBodyAccJerk.std.Y           |
|                     |                                      |                   |fBodyAccJerk.std.Z           |
|                     |                                      |                   |fBodyAccMag.mean             |
|                     |                                      |                   |fBodyAccMag.meanFreq         |
|                     |                                      |                   |fBodyAccMag.std              |
|                     |                                      |                   |fBodyBodyAccJerkMag.mean     |
|                     |                                      |                   |fBodyBodyAccJerkMag.meanFreq |     
|                     |                                      |                   |fBodyBodyAccJerkMag.std      |      
|                     |                                      |                   |fBodyBodyGyroJerkMag.mean    |
|                     |                                      |                   |fBodyBodyGyroJerkMag.meanFreq|
|                     |                                      |                   |fBodyBodyGyroJerkMag.std     |
|                     |                                      |                   |fBodyBodyGyroMag.mean        |
|                     |                                      |                   |fBodyBodyGyroMag.meanFreq    |
|                     |                                      |                   |fBodyBodyGyroMag.std         |
|                     |                                      |                   |fBodyGyro.mean.X             |
|                     |                                      |                   |fBodyGyro.mean.Y             |
|                     |                                      |                   |fBodyGyro.mean.Z             |
|                     |                                      |                   |fBodyGyro.meanFreq.X         |
|                     |                                      |                   |fBodyGyro.meanFreq.Y         |
|                     |                                      |                   |fBodyGyro.meanFreq.Z         |
|                     |                                      |                   |fBodyGyro.std.X              |
|                     |                                      |                   |fBodyGyro.std.Y              |
|                     |                                      |                   |fBodyGyro.std.Z              |
|                     |                                      |                   |tBodyAcc.mean.X              |
|                     |                                      |                   |tBodyAcc.mean.Y              |
|                     |                                      |                   |tBodyAcc.mean.Z              |
|                     |                                      |                   |tBodyAcc.std.X               |
|                     |                                      |                   |tBodyAcc.std.Y               |
|                     |                                      |                   |tBodyAcc.std.Z               |
|                     |                                      |                   |tBodyAccJerk.mean.X          |
|                     |                                      |                   |tBodyAccJerk.mean.Y          |
|                     |                                      |                   |tBodyAccJerk.mean.Z          |
|                     |                                      |                   |tBodyAccJerk.std.X           |
|                     |                                      |                   |tBodyAccJerk.std.Y           |
|                     |                                      |                   |tBodyAccJerk.std.Z           |
|                     |                                      |                   |tBodyAccJerkMag.mean         |
|                     |                                      |                   |tBodyAccJerkMag.std          |
|                     |                                      |                   |tBodyAccMag.mean             |
|                     |                                      |                   |tBodyAccMag.std              |
|                     |                                      |                   |tBodyGyro.mean.X             |
|                     |                                      |                   |tBodyGyro.mean.Y             |
|                     |                                      |                   |tBodyGyro.mean.Z             |
|                     |                                      |                   |tBodyGyro.std.X              |
|                     |                                      |                   |tBodyGyro.std.Y              |
|                     |                                      |                   |tBodyGyro.std.Z              |
|                     |                                      |                   |tBodyGyroJerk.mean.X         |
|                     |                                      |                   |tBodyGyroJerk.mean.Y         |
|                     |                                      |                   |tBodyGyroJerk.mean.Z         |
|                     |                                      |                   |tBodyGyroJerk.std.X          |
|                     |                                      |                   |tBodyGyroJerk.std.Y          |
|                     |                                      |                   |tBodyGyroJerk.std.Z          |
|                     |                                      |                   |tBodyGyroJerkMag.mean        |
|                     |                                      |                   |tBodyGyroJerkMag.std         |
|                     |                                      |                   |tBodyGyroMag.mean            |
|                     |                                      |                   |tBodyGyroMag.std             |
|                     |                                      |                   |tGravityAcc.mean.X           |
|                     |                                      |                   |tGravityAcc.mean.Y           |
|                     |                                      |                   |tGravityAcc.mean.Z           |
|                     |                                      |                   |tGravityAcc.std.X            |
|                     |                                      |                   |tGravityAcc.std.Y            |
|                     |                                      |                   |tGravityAcc.std.Z            |
|                     |                                      |                   |tGravityAccMag.mean          |
|                     |                                      |                   |tGravityAccMag.std           |
|                     |                                      |                   |                             |
| mean.value          |Mean value of the feature parameters  | Double            |Value between -1 and 1       |
|                     |                                      |                   |(Features are normalized)    |


```{r cars}
```


