---
title: "CodeDescription"
author: "ThierryFauret"
date: "5 février 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The object of this file is to describe to ru_analysis.R code :

```{r}
library(dplyr)
library(tidyr)
library(lubridate)

urlb<-"https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(urlb,"data.zip",method="libcurl")
unzip("data.zip")


# READING OF TRAINING DATA

# number of the subject from 1 to 30
subject.train<-read.table("UCI HAR Dataset/train/subject_train.txt")

# list of performances for each futures
x.train<-read.table("UCI HAR Dataset/train/X_train.txt")

#activity from 1 to 6
y.train<-read.table("UCI HAR Dataset/train/y_train.txt")



# READING OF TEST DATA

# number of the subject from 1 to 30
subject.test<-read.table("UCI HAR Dataset/test/subject_test.txt")
# list of performances for each futures
x.test<-read.table("UCI HAR Dataset/test/X_test.txt")
#activity from 1 to 6
y.test<-read.table("UCI HAR Dataset/test/y_test.txt")


```
WE read the name of features and keep only labels with "mean" and "std""

```{r}
#READING OF FEATURES DATA

list.features<-read.table("UCI HAR Dataset/features.txt")

#We keep only the features for whose labels contain mean of std
list.features<-list.features[grep("mean|std", list.features[,2]),]

```

We clean the label of features by removing "-" and parentesis.

```{r}
# Cleaning the labels by removing the parentessis and the "-"
list.features[,2]<-gsub("-",".",list.features[,2])
list.features[,2]<-gsub("\\()","",list.features[,2])

# calcul of the new number of features analyzed (with mean and std)

nb.features<-nrow(list.features)

```

We filter the intial data (only feature with mean and std in the name)

```{r}
# Filter on mean and STD values given for the different features

x.test<-x.test[,list.features[,1]]
x.train<-x.train[,list.features[,1]]

```

List of the activities
```{r}
#READING OF ACTIVITIES TABLE : WALKING, WLAKING_UPSTAIRS

list.activities<-read.table("UCI HAR Dataset/activity_labels.txt")
colnames(list.activities)<-c("nb.activity","label.activity")
print(list.activities)
```

We merge the data in order to have an unique data base :

```{r}
# MERGING DIFFRENT DATA bASES TO HAVE AN UNIQUE DATA BASE WITH
#     *  train data
#     *  test data
#     *  labels of activity

bdd.train<-cbind(subject.train,y.train,x.train)
colnames(bdd.train)<-c("subject","activity",list.features[1:nrow(list.features),2])
bdd.test<-cbind(subject.test, y.test,x.test)
colnames(bdd.test)<-c("subject","activity",list.features[1:nrow(list.features),2])
bdd<-rbind(bdd.train,bdd.test) %>%
merge(list.activities,by.x="activity",by.y="nb.activity") %>%
select(- activity)
print(head(bdd,2))
```

Calcul of the mean for each subject, each activity and each feature :

```{r}
#############################################
# STEP 2 of the assignment 
#############################################
#############################################
# STEP 2 of the assignment 
#############################################

bdd2<-aggregate(.~subject+label.activity,data=bdd,mean)
print(head(bdd,2))

# Writting of the results in tidydata.txt
write.table(bdd2, file = "tidydata.txt",row.name=FALSE)

```



